Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-01-24 RNARedPrint.tex
Responded to Stefan's comments

%\paragraph{Central computational problem.}
Let us consider $m$ (secondary) structures $R_1,\dots, R_m$, each abstracted as a set of base pairs, and \revised{$k\geq m$} features $F_1,\dots, F_k$, associated with weights $\pi_1,\dots,\pi_k$. Our goal is to sample from the Boltzmann distribution, defined over the set of sequences that satisfy classic base pairing rules for each structure as: 
\todo{$S$ sequence not defined!}
\begin{equation}
\label{eq:sample-distribution}
\Pr(S\mid\pi_1,\dots,\pi_k) \propto \displaystyle\prod_{1\leq \ell\leq k}\!\! \pi_\ell^{-F_\ell(S)} \end{equation}

@@

\subsection*{Expressing \GCb\%-content, sequence validity and energies as features}
\todo{$x_1$ position(?) not defined!\\$S_x_1$ nucleotide at position(?) not defined!\\$p$ number of dependent positions(?) from $x_p$ not defined!}
Formally, we define a \Def{feature $F$} as a function on sequences, whose value is obtained by summing over an associated set of \Def{contributions}. Each contribution $f$ takes values in $\mathbb{R}\cup \{+\infty\}$, and depends on the nucleotides assigned to a restricted set of positions, its \emph{dependencies $\dep(f)$}, such that
$$
F(S) =\!\!\!\!\!\!\!\sum_{\substack{\text{$f$ contribution of $F$,}\\\text{ $\dep(f)=\{x_1,\ldots,x_p\}$}}}\!\!\!\!\!\! f\left(\left\{\substack{x_1\mapsto S_{x_1}\\\cdots\\x_p\mapsto S_{x_p}}\right\}\right).
$$

The $\GCb\%$ can be simply expressed using $n$ contributions $f^{\GCb}_i$, $i\in[1,n]$, whose dependencies are restricted to individual nucleotides,  and such that 
$$f^{\GCb}_i(\{i\mapsto c\})=\begin{cases}-1&\text{ if }c=\Gb\text{ or }\Cb\\ 0&\text{ otherwise}.\end{cases}$$ 
\todo{Why here $i$ and not $x_i$??}
\revised{By summing $f^{\GCb}_i(\{i\mapsto S_i\})$ over the whole sequence, one simply counts the occurrences of $\Gb$ and $\Cb$.}

>>>>

%\paragraph{Central computational problem.}
Let us consider $m$ (secondary) structures $R_1,\dots, R_m$, each abstracted as a set of base pairs, and \revised{$k\geq m$} features $F_1,\dots, F_k$, associated with weights $\pi_1,\dots,\pi_k$. Our goal is to sample from the Boltzmann distribution, such that the probability of a sequence $S\in \Sigma^\star$ of length $n$, within the set of sequences that satisfy classic base pairing rules, is defined as: 
\todo{$S$ sequence not defined!}
\begin{equation}
\label{eq:sample-distribution}
\Pr(S\mid\pi_1,\dots,\pi_k) \propto \displaystyle\prod_{1\leq \ell\leq k}\!\! \pi_\ell^{-F_\ell(S)} \end{equation}

@@

\subsection*{Expressing \GCb\%-content, sequence validity and energies as features}
\todo{$x_1$ position(?) not defined!\\$S_{x_1}$ nucleotide at position(?) not defined!\\$p$ number of dependent positions(?) from $x_p$ not defined!\\
Yann: We just defined the dependencies as positions in the sequence, so $x_i$ should be fine from the context. $p$ is purely declarative (it differs for each $f$), so it should be ok, but since it is unused, we can probably drop it...
}
Formally, we define a \Def{feature $F$} as a function on sequences, whose value is obtained by summing over an associated set of \Def{contributions}. Each contribution $f$ takes values in $\mathbb{R}\cup \{+\infty\}$, and depends on the nucleotides assigned to a restricted set of positions, its \emph{dependencies $\dep(f)$}, such that 
$$
F(S) =\!\!\!\!\!\!\!\sum_{\substack{\text{$f$ contribution of $F$,}\\\text{ $\dep(f)=\{x_1,x_2,\ldots\}$}}}\!\!\!\!\!\! f\left(\left\{\substack{x_1\mapsto S_{x_1}\\x_p\mapsto S_{x_2}\\\cdots}\right\}\right).
$$
where any $x_i \in [1,n]$ represents a position in $S$, and $S_x$ represents the letter found at position $x$ in $S$.

The $\GCb\%$ can be simply expressed using $n$ contributions $f^{\GCb}_i$, $i\in[1,n]$, whose dependencies are restricted to individual nucleotides,  and such that 
$$f^{\GCb}_i(\{i\mapsto c\})=\begin{cases}-1&\text{ if }c=\Gb\text{ or }\Cb\\ 0&\text{ otherwise}.\end{cases}$$ 
\todo{Why here $i$ and not $x_i$??\\Yann: Because $x_1$, $x_2$... was just a way to talk about the first, second... argument of a function having an arbitrary number of args. Here, there is just one, so no need for subscripts.}
\revised{By summing $f^{\GCb}_i(\{i\mapsto S_i\})$ over the whole sequence, one simply counts the occurrences of $\Gb$ and $\Cb$.}
